Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-07 longSC.tex
remove old low order

\begin{figure*}[!]
            \begin{center}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT_backup.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT_backup.eps}}
                \end{center}
        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
        \label{fig:Figure_5_0}
\end{figure*}

>>>>

%\begin{figure*}[!]
%            \begin{center}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT_backup.eps}}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT_backup.eps}}
%                \end{center}
%        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
%        \label{fig:Figure_5_0}
%\end{figure*}
%
